Concurrent Programming with CXL

### 2020-05-17 book/paper.tex
Latest version

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: when every process
that is in the critical section eventually leaves it, then any process
that tries to enter the critical section should eventually be able to do so.
We call this \emph{progress}.

>>>>

Mutual exclusion is an example of a \emph{safety property}, a
property that ensures that \emph{nothing bad will happen}, in this case
two processes being in the critical section.
What we need now a \emph{liveness property}: we want to ensure that
\emph{eventually something good will happen}.
There are various possible liveness properties we could use,
but here we will propose the following informally: if some set of processes
$S$ are trying to enter the critical section, then eventually one process in
$S$ will enter the critical section if any process already in the
intersection eventually leaves, even if no processes other than $S$ ever
try to enter the critical section.
We call this \emph{progress}.

% from any state some process should be able to eventually enter the
% critical section.  Without the help of any processes that reach ncs
% (but don't start there).
